Testing atlantisom: generate census length comps

### 2019-05-11 TrueLengthCompTest.Rmd
adjustments for the next run
it worked!

@@

```{r allspplength}

@@

@@

>>>>

# try dir = "v" option for vertical lf comparisons

@@

```{r allspplength, eval=FALSE}

@@

#save for later use, takes a long time to generate
saveRDS(length_censussurvsamp, file.path(d.name, paste0(scenario.name, "length_censussurvsamp.rds")))

@@

Answer: this ran for 5.5 hours. But it was really only 5 hours 20 minutes that was the last code block! Saving the file is highly recommended.
